Standard Candle Cosmology With Incomplete Spectroscopic Classification

### 2015-10-18 doc/article.tex
more fixes

@@

\section{DES SN Survey Model}
\label{snIamodel:sec}
\subsection{Model}
SNe~Ia are not perfect standard candles but rather are calibrated candles whose
peak brightnesses are a
function of their internal properties discerned from their colors and light-curve evolution.
Measurement uncertainty, particularly from photometric flux
calibration and galaxy photometric redshifts, can play an important role in the statistical
reach of experiments.  This Section contains a model that expands upon the one
presented in \S\ref{snIamodel:sec} to have the fidelity needed for the photometric
supernova analysis of the Dark Energy Survey and the Large Synoptic Survey Telescope.

The notation for the likelihood presents the data and fundamental model parameters
\begin{equation}
p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g),
\label{likelihood2:eqn}
\end{equation}
whose relations are sketched in the probabilistic graphical model in Figure~\ref{pgm:fig}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.5in]{/Users/akim/project/abc/results/hdpgm.pdf} 
   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
   The forward modeling
   flow goes from left to right, starting with the description of the universe, observatory,
   and data.    A transient has host galaxy $g_i$, which determines its redshift $z_i$
   and galaxy parameters $\theta_{gi}$.
   A model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
   The transient type $T$ depends on the host-galaxy parameters  $\theta_{gi}$
   and rates $\theta_r$.   The transient
   parameters $\theta_T^X$, $\theta_{Ti}^X$ (and perhaps the host galaxy) determine the luminosity $L$.       The 
   incoming photon flux $n$, $n_g$  are then fixed
   with redshift and distance modulus.
   The instrumental transmission function $\phi$ is calibrated with data ${Z}$ andflux
   gives the expected
   counts $\overline{f}$, $\overline{f}_g$. 
   The transient has realized light curves (${ADU}$) and passes selection criteria
   through $\tau_i$ to be included in the sample.  Some transients have spectral data
   ${X}_S$.  The properties of the galaxy identified as the host galaxy is $\theta_G$. 
   \label{pgm:fig}}
\end{figure}

The new measurement that differs from  \S\ref{model:sec} is
\begin{itemize}
\item $\mathit{ADU}$: the measured counts for each photometric observation.
This takes
the place of flux as calibration is now considered.
\end{itemize}
The new model parameters are
\begin{itemize}
\item $Z$: the parameters that describe the transmission functions, i.e.\ photometric calibration.
\item $\beta_{Ia}$, $\beta_{non-Ia}$: the parameters for the internal diversity within SNe~Ia and
non-Ia's respectively, e.g.\ SALT2's  $\alpha$ and $\beta$;
\item $f_g$: the surface brightness of the background light at the location of the transient
needed for to extract the photometry of the point-source transient.
\end{itemize}
New latent model parameters for each transient:
\begin{itemize}
\item $\theta_{Ia}$, $\theta_{non-Ia}$: the transient parameters that describe individual
transients, e.g.\ SALT2's $x_1$, $c$;
\item $g$: the parameters that describe the candidate host and neighbor galaxies,
to be more expansive than the previous $z$ parameter.
\end{itemize}
The new fixed parameters are
\begin{itemize}
\item{$f$}: the flux of the transient;
\item{$\overline{\mathit{ADU}}_X$}: the expected counts of the transient and background light.
\end{itemize}

\begin{itemize}
\item Intrinsic transient parameters are dependent on their distributions and the host galaxy.
The SNe~Ia parameters are drawn as
\begin{equation}
\theta_{Ia} | \sigma_{Ia}, g \sim \mathcal{N}(0, \sigma_{Ia}),
\end{equation}
where $\theta_{Ia} =\{x_1, c, \delta_M\}$, the SALT2 light-curve shape and color parameters.
A more complex model can be based on non-Normal distributions
and/or including SN properties directly tied to characteristics (e.g.\ mass, star formation
rate) of the host galaxy.

The non-Ia parameters are drawn as
\begin{equation}
\theta_{non-Ia} | \sigma_{non-Ia}, g  \sim \mathcal{N}(0, \sigma_{non-Ia}),
\end{equation}
where the parameter is the realization of an intrinsic magnitude dispersion.
A more complex model can include multiple non-Ia populations each with its own
intrinsic parameters.
\item Spectroscopically observed transient parameters depend on the intrinsic transient
parameters and type.  $\theta_{Si}$ may be ignored in a zero'th order analysis that
does not relate spectral features with SN~Ia absolute magnitudes.   If spectral
features are considered, the simple model
\begin{equation}
\theta_{Si} | \theta_{Ia}, \theta_{non-Ia}, T = \delta(\theta_{Si}-\theta_T)
\end{equation}
assumes an unambiguous mapping between supernova parameters and spectral signal.
\item The type is drawn from the host-dependent relative rate between SNe~Ia and non-Ia's 
\begin{equation}
T | \theta_r, g \sim \rm{Bernoulli}(\pi(g,\theta_r)),
\end{equation}
where $\pi$ is a model for the relative rates of the different types as a
function of galaxy parameters and redshift.  A reasonable choice for $\pi$ needs to be
selected, any volunteers?
\item Supernova type is assumed to be unambiguously encoded in the
spectrum:
\begin{equation}
T_S | T  = \delta(T_S - T).
\end{equation}
\item The observed redshift is taken to be the host galaxy redshift
\begin{equation}
z_S = g_z,
\end{equation}
where $g_z$ is the element in $g$ that corresponds to redshift.
Added sophistication includes redshift
measurement uncertainty and random peculiar velocities. The study of coherent
flow requires added model complexity.
\item The underlying SED of transients are modeled.  For SNe~Ia the SALT2 model
is an option, although new models that separate dust and intrinsic color or
identify new SN~Ia parameters are expected in the near future.  Absolute magnitudes
that depend on host-galaxy properties need to be considered. 
For SNe~Ia $T=1$
\begin{equation}
L(t,\lambda; \alpha_{Ia}, \beta_{Ia}, \theta_{Ia}, g)  =10^{-\left(\frac{\alpha x_1 + \beta c}{2.5}\right)}L_{SALT2}(t-t_0; \alpha_{Ia}, x_1, c, \delta_m) \gamma(g, \beta) ,
\end{equation}
where the first two terms is the SALT2 model with a realized error snake,
and $\gamma(g, \beta)$ a step function with free parameters in $\beta$ that
describe the step size.

For non-Ia's $T=0$ a set of light curve templates or a model can be used.
An initial candidate is the treatment of non-Ia's implemented in PSNID.
\item The theoretical distance modulus
\begin{equation}
\mu(g_z; \Omega_M, w)
\end{equation}
is the predicted distance modulus of a flat dark energy cosmology.
\item The flux incident on Earth is the redshifted and time-dilated SED scaled
by the distance modulus.
\begin{equation}
f(t,\lambda) = 10^{-\mu/2.5} L\left(t/(1+g_z),\lambda/(1+g_z)\right)
\end{equation}
\item The expected light curve in counts depends on the flux and throughput of the
optical chain.  A first model encapsulates flux calibration through a zeropoint
\begin{equation}
\overline{\mathit{ADU}}(f, Z) = 10^{Z/2.5} \int  f(\lambda) T_0(\lambda)d\lambda,
\end{equation}
where $T_0$ is a fiducial transmission function for the appropriate filter.  A more sophisticated
analysis can have a transmission function specific to each observation.
\item The measured surface brightness of the host galaxy depends on the underlying
surface brightness convolved with the point spread function and integrated
over the transmission
\begin{equation}
\overline{\mathit{ADU}}_g =    \int (f_g(\lambda, RA, Dec) \otimes PSF) T(\lambda;Z)d\lambda.
\end{equation}
\item The measurement $\mathit{ADU}$ is the superposition of transient and background
light $\overline{\mathit{ADU}} + \overline{\mathit{ADU}}_g$.
\end{itemize}

\subsection{Measurements}
\label{measurements:sec}
In the following discussion,
spectroscopic and galaxy measurements are assumed
to provide prefect determinations of transient type and parameters, and
galaxy redshifts and parameters. 
\begin{align}
p(T_S|T) &= \delta(T_S-T),\\
p(\theta_S|\theta_T) &= \delta(\theta_S|\theta_T),\\
p(\theta_G|g) &= \delta(\theta_G-g)\\
p(z_S|g_z) &= \delta(z_S-g_z)\\.
\label{specz:eqn}
\end{align}
The working group is striving to get spectroscopic
redshifts of all potential hosts.  People who are interested in SN spectral features
or host-galaxy correlations (Chris, Rachel, Mat) can develop these models.

The measured counts depend on the expected counts and measurement uncertainty
$C_P$ as a Poisson (or considering the high sky background Normal) distribution
\begin{equation}
\mathit{ADU} \sim \mathcal{N} (\overline{\mathit{ADU}}+\overline{\mathit{ADU}}_g ,C_P).
\label{ADU:eqn}
\end{equation}
Practically, the photometric extraction is handled by independent software, which calculates
the pdf of $\mathit{ADU}_{\mathit{SN}}$, the realized contribution of supernova light,
replacing this and the previous two bullet points.  Dillon is providing this.
For the rest of the discussion, $\mathit{ADU}_{\mathit{SN}}$ is treated a measurement
directly connected to the expected mean signal of the supernova
$\overline{\mathit{ADU}}$
\begin{equation}
\mathit{ADU}_{SN} \sim \mathcal{N} (\overline{\mathit{ADU}} ,C_P).
\end{equation}

\subsection{Constructing the Likelihood}

%The likelihood for the analysis sample is related to the underlying likelihood through
%\begin{multline}
%p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
%= \frac{\epsilon(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G) p_U(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | \ldots)}
%{\sum_{T_S} \int d\mathit{ADU}\, dz_S\, d\theta_S\, d\theta_G\, \epsilon(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G) p_U(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | \ldots)},
%\end{multline} 
%where $p_U$ is the underlying likelihood  and $\epsilon$ is the efficiency for inclusion
%in the sample (more precisely subsample as spectroscopic
%selection should produce different efficiencies for the {\it obs} and {\it mis} sets.)

The following is a sketch of the likelihood calculation for an example 
photometric selection criterion, which should serve as a useful guide once the criteria are fixed.
The criterion is for $\ge N$ photometric points
above a signal-to-noise threshold (translating to a distinct limiting signal $ADU_{0i}$
for measurement $i$ of a given transient) given $M$ available measurements. 
The fail/pass status of the measurements are stored as 0/1 in an array $b$.
There are $\sum_{k=N}^M \binom{M}{k}$ 
distinct $b$'s that allow acceptance of the light curve.  In the notation $b_{ijk}$, $i$ indexes
the configuration, $j$ the transient, and $k$ the photometric point of transient $j$.

\subsubsection{Likelihood for the {\it obs} Set}
The likelihood for the {\it obs} set is
\begin{multline}
p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
= \sum_i \int_L dL\, p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G , b_i|  L, \ldots)
 P(L|\ldots) \\
 \propto \sum_i  \epsilon(\mathit{ADU}_{SN}; b_{i}) \int_L dL\, p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G|  L, \ldots)P(L|\ldots).
\end{multline} 
It is proportional to the truncated likelihood of the underlying sample, where the truncation
is achieved through $\epsilon(\mathit{ADU}_{SN}; b_{i})$, the efficiency that a light curve is 
selected in for a given configuration.  For the limiting flux criteria
\begin{equation}
\epsilon(\mathit{ADU}_{SN}; b_{i})= \prod_{jk}\mathcal{H}\left((-1)^{b_{ijk}+1}(ADU_{SN,jk}-ADU_{0,jk})\right),
\end{equation}
where $\mathcal{H}$ is the Heaviside step function; when $b_{ijk}=1$ the step in the efficiency
is up and for $b_{ijk}=0$ the step is down.

%The likelihood without the configuration condition for our measurements is
%\begin{multline}
%p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots) \\
%= \delta(z_S - g_z) \delta(\theta_S-\theta_T) \delta(\theta_G -g) \delta(T_S-T)  \mathcal{N}
%\left(\mathit{ADU}_{SN} -\overline{\mathit{ADU}}_j(L ,\ldots), C_P \right).
%\end{multline}. 
%

%
%The probability for failing (passing) the selection criterion for a single point is
%\begin{equation}
%P(b_{ij} | L, \ldots) = b_{ij} + (-1)^{b_{ij}}\int_{-\infty}^{ADU_0} d\mathit{ADU}_{SN,i}  \mathcal{N}\left(\mathit{ADU}_{SN} - \overline{\mathit{ADU}}_j(L ,\ldots), C_P \right),
%\end{equation}
%the (complementary) cumulative distribution function for a normal distribution
%with variable
%$\mathit{ADU}_0$, i.e.\ 2 times the error function.

For measurements described in \S\ref{measurements:sec}, the likelihood for the {\it obs} Set is
\begin{multline}
p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
\propto \sum_i  \epsilon(\mathit{ADU}_{SN}; b_{i})  \int_L dL\, 
\mathcal{N}\left(\mathit{ADU}_{SN} - \overline{\mathit{ADU}}_j(L ,
g_z=z_S, \theta_T=\theta_S, g=\theta_G, T=T_S, \ldots), C_P \right)\\
P(L|g_z=z_S, \theta_T=\theta_S, g=\theta_G, T=T_S, \ldots),
\end{multline} 
where the latent parameters $T$, $\theta_T$ are not integrated over.
The normalization factor is parameter-dependent and is set by the condition
\begin{equation}
\sum_{T_S} \int d\mathit{ADU}_{SN}\,d{{z}}_S\,d\theta_{S}\,d\theta_G\,p(\mathit{ADU}_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \ldots)=1.
\end{equation}

\subsubsection{Likelihood for the {\it mis} Set}
The likelihood for the {\it mis} set follow the same pattern as that of the
{\it obs} set except for not having to account for spectroscopic data.
\begin{multline}
p(\mathit{ADU}_{SN}, \theta_{G_1} |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g) \\
 \propto \sum_i  \epsilon(\mathit{ADU}_{SN}; b_{i}) 
\int_L dL\, 
\sum_k 
\pi_k\mathcal{N}\left(\mathit{ADU}_{SN} - \overline{\mathit{ADU}}_j(L ,
g=\theta_{G_k}, \ldots), C_P \right)
P(L|g=\theta_{G_k}, \ldots), 
\end{multline} 
where $\pi_k$ is the probability that the $k$'th galaxy is the host, provided by Ravi.

>>>>

\section{DES SN Survey Model}
\label{snIamodel:sec}
\subsection{Model}
This Section presents a candidate model
for supernova surveys that has the fidelity needed for the photometric
supernova analysis of the Dark Energy Survey and the Large Synoptic Survey Telescope.
%SNe~Ia are not perfect standard candles but rather are calibrated candles whose
%peak brightnesses are a
%function of their internal properties discerned from their colors and light-curve evolution.
%Measurement uncertainty, particularly from photometric flux
%calibration and galaxy photometric redshifts, can play an important role in the statistical
%reach of experiments. 
The notation for the likelihood presents the data and fundamental model parameters
\begin{equation}
p(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  \sigma_\beta, Z, g, g_N, f_g),
\label{likelihood2:eqn}
\end{equation}
whose relations are sketched in the probabilistic graphical model in Figure~\ref{pgm:fig}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.5in]{/Users/akim/project/abc/results/hdpgm.pdf} 
   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
   The forward modeling
   flow goes from left to right, starting with the description of the universe, observatory,
   and data.    A transient has host galaxy $g_i$, which determines its redshift $z_i$
   and galaxy parameters $\theta_{gi}$.
   A model with parameters $\theta_\mu$ fix the distance modulus $\mu_i$.
   The transient type $T$ depends on the host-galaxy parameters  $\theta_{gi}$
   and rates $r$.   The transient
   parameters $\theta_T^X$, $\theta_{Ti}^X$ (and perhaps the host galaxy) determine the luminosity $L$.       The 
   incoming photon flux $n$, $n_g$  are then fixed
   with redshift and distance modulus.
   The instrumental transmission function $\phi$ is calibrated with data ${Z}$ andflux
   gives the expected
   counts $\overline{f}$, $\overline{f}_g$. 
   The transient has realized light curves ($n$) and passes selection criteria
   through $\tau_i$ to be included in the sample.  Some transients have spectral data
   ${X}_S$.  The properties of the galaxy identified as the host galaxy is $\theta_G$. 
   \label{pgm:fig}}
\end{figure}

The measurements are
\begin{itemize}
\item $n$: the measured counts for each photometric observation;
\item ${{T}}_S$, ${{z}}_S$, $\theta_S$: the spectroscopic type, redshift, and transient parameters available for a subset of transients;
\item $\theta_{G1}$, $\theta_{G2}$: the spectroscopic redshifts of the galaxies identified
as host and neighbor from imaging.
\end{itemize}
The model parameters are
\begin{itemize}
\item $\Omega_M$, $w$: the mass density and dark-energy equation of state parameters of a flat,
constant-$w$ dark-energy cosmology;
\item $r_1$, $r_2$:  the parameters
that describe the redshift-dependent relative fraction of SNe~Ia and non-Ia's;
\item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{non-Ia}}$, $\sigma_{\mathit{non-Ia}}$:
the luminosity (times $4\pi$) and intrinsic dispersion for SNe~Ia and non-Ia at peak brightness;
\item $\beta_{Ia}$, $\beta_{non-Ia}$: the parameters for the internal diversity within SNe~Ia and
non-Ia's respectively, e.g.\ SALT2's  $\alpha$ and $\beta$;
\item $\sigma_\beta$: parameters that describe the distribution of intrinsic supernova
parameters of SNe~Ia and non-Ia;
\item $Z$: the parameters that describe the transmission functions, i.e.\ photometric calibration;
\item $g$, $g_N$: the parameters that describe the candidate host and neighbor galaxies,
to be more expansive than the previous $z$ parameter;
\item $f_g$: the surface brightness of the background light at the location of the transient
needed for to extract the photometry of the point-source transient.
\end{itemize}
Not listed explicitly in Eqn.~\ref{likelihood:eqn} but shown in Figure~\ref{toypgm:fig} are latent model parameters for each transient:
\begin{itemize}
%\item $z$: the cosmological redshifts of the host and neighboring galaxies;
\item $T$: the class of the objects, SN~Ia or non-Ia;
\item $\theta_{Ia}$, $\theta_{non-Ia}$: the transient parameters that describe individual
transients, e.g.\ SALT2's $x_1$, $c$;
\item $L$: the luminosity of the transient.
\end{itemize}
There are  fixed parameters
\begin{itemize}
\item $\mu$: the distance modulus given the cosmological parameters and the redshift;
\item{$f$}: the flux of the transient given the luminosity, distance modulus, and
redshift;
\item{$\overline{n}_X$}: the expected counts of the transient and background light given
the flux and transmission.
\end{itemize}

\begin{itemize}
\item Intrinsic transient parameters are dependent on their distributions and the host galaxy.
The SNe~Ia parameters are drawn as
\begin{equation}
\theta_{Ia} | \sigma_\beta, g \sim \mathcal{N}(0, \sigma_{\beta,Ia}),
\end{equation}
where $\theta_{Ia} =\{x_1, c\}$ are the SALT2 light-curve shape and color parameters.
A more complex model can be based on non-Normal distributions
and/or including SN properties directly tied to characteristics (e.g.\ mass, star formation
rate) of the host galaxy.

{\bf The non-Ia parameters, their underlying distributions, and SED's need to chosen.}
The prime candidate
is their description used in PSNID.

%\begin{equation}
%\theta_{non-Ia} | \sigma_\beta, g  \sim \mathcal{N}(0, \sigma_{\beta, non-Ia}),
%\end{equation}
%where the parameter is the realization of an intrinsic magnitude dispersion.
%A more complex model can include multiple non-Ia populations each with its own
%intrinsic parameters.
\item Spectroscopically observed transient parameters depend on the intrinsic transient
parameters and type.  $\theta_{Si}$ may be ignored in a zero'th order analysis that
does not relate spectral features with SN~Ia absolute magnitudes.   If spectral
features are considered, the simple model
\begin{equation}
\theta_{Si} (\theta_{Ia}, \theta_{non-Ia}, T)=\theta_T
\end{equation}
assumes an unambiguous mapping between supernova parameters and spectral signal.
{\bf We need to decide what SN spectral parameters, if any, we will consider in our analysis.}
\item The type is drawn from the host-dependent relative rate between SNe~Ia and non-Ia's 
\begin{equation}
T | r, g \sim \rm{Bernoulli}(\pi(g,r)),
\end{equation}
where $\pi$ is a model for the relative rates of the different types as a
function of galaxy parameters and redshift.  {\bf A reasonable choice for $\pi$ needs to be
selected, any volunteers?}
\item Supernova type is assumed to be unambiguously encoded in the
spectrum:
\begin{equation}
T_S (T)  = T.
\end{equation}
\item The observed redshift is taken to be the host galaxy redshift
\begin{equation}
z_S (g_z) =g_z
\end{equation}
where $g_z$ is the element in $g$ that corresponds to redshift.
Added sophistication includes redshift
measurement uncertainty and random peculiar velocities. The study of coherent
flow requires added model complexity.
\item The underlying SED of transients are modeled.  For SNe~Ia the SALT2 model
is an option, although new models that separate dust and intrinsic color or
identify new SN~Ia parameters are expected in the near future.  Absolute magnitudes
that depend on host-galaxy properties need to be considered. 
For SNe~Ia $T=1$
\begin{equation}
L(t,\lambda) |  \alpha_{Ia}, \beta_{Ia}, \sigma_{Ia},  \theta_{Ia}, g, x_1, c \sim L_{SALT2}(t-t_0; \alpha_{Ia}, x_1, c) \gamma(g, \beta) \mathcal{N}(0,\sigma_{Ia}),
\end{equation}
where the first  term is the SALT2 light-curve and absolute magnitude
model with a realized error snake,
and $\gamma(g, \beta)$ a step function with free parameters in $\beta$ that
describe the step size.

{\bf The non-Ia model needs to be identified.}
\item The theoretical distance modulus
\begin{equation}
\mu(g_z; \Omega_M, w) = \mu_{wCDM}(g_z; \Omega_M, w)
\end{equation}
is the predicted distance modulus of a flat dark energy cosmology.
\item The flux incident on Earth is the redshifted and time-dilated SED scaled
by the distance modulus.
\begin{equation}
f(t,\lambda; L) = 10^{-\mu/2.5} L\left(t/(1+g_z),\lambda/(1+g_z)\right)
\end{equation}
\item The expected light curve in counts depends on the flux and throughput of the
optical chain.  A first model encapsulates flux calibration through a zeropoint
\begin{equation}
\overline{n}(f, Z) = 10^{Z/2.5} \int  f(\lambda) T_0(\lambda)d\lambda,
\end{equation}
where $T_0$ is a fiducial transmission function for the appropriate filter.  A more sophisticated
analysis can have a transmission function specific to each observation.
\item The measured surface brightness of the host galaxy depends on the underlying
surface brightness convolved with the point spread function and integrated
over the transmission
\begin{equation}
\overline{n}_g =    \int (f_g(\lambda, RA, Dec) \otimes PSF) T(\lambda;Z)d\lambda.
\end{equation}
\item The measurement $n$ is the superposition of transient and background
light $\overline{n} + \overline{n}_g$.
\end{itemize}

\subsection{Measurements}
\label{measurements:sec}
In the following discussion,
spectroscopic and galaxy measurements are assumed
to provide prefect determinations of transient type and parameters, and
galaxy redshifts and parameters. 
\begin{align}
p(T_S|T) &= \delta(T_S-T),\\
p(\theta_S|\theta_T) &= \delta(\theta_S-\theta_T),\\
p(\theta_G|g) &= \delta(\theta_G-g),\\
p(z_S|g_z) &= \delta(z_S-g_z)
\label{specz:eqn}
\end{align}
The working group is striving to get spectroscopic
redshifts of all potential hosts.  People who are interested in SN spectral features
or host-galaxy correlations (Chris, Rachel, Mat) can develop these models.

The measured counts depend on the expected counts and measurement uncertainty
$C_P$ as a Poisson (or considering the high sky background Normal) distribution
\begin{equation}
n \sim \mathcal{N} (\overline{n}+\overline{n}_g ,C_P).
\label{ADU:eqn}
\end{equation}
Practically, the photometric extraction is handled by independent software, which calculates
the pdf of $n_{\mathit{SN}}$, the realized contribution of supernova light,
replacing this and the previous two bullet points.  Dillon is providing this.
For the rest of the discussion, $n_{\mathit{SN}}$ is treated a measurement
directly connected to the expected mean signal of the supernova
$\overline{n}$
\begin{equation}
n_{SN} \sim \mathcal{N} (\overline{n} ,C_P).
\end{equation}

Prior on $Z$.
\subsection{Constructing the Likelihood}

%The likelihood for the analysis sample is related to the underlying likelihood through
%\begin{multline}
%p(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
%= \frac{\epsilon(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G) p_U(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | \ldots)}
%{\sum_{T_S} \int dn\, dz_S\, d\theta_S\, d\theta_G\, \epsilon(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G) p_U(n, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | \ldots)},
%\end{multline} 
%where $p_U$ is the underlying likelihood  and $\epsilon$ is the efficiency for inclusion
%in the sample (more precisely subsample as spectroscopic
%selection should produce different efficiencies for the {\it obs} and {\it mis} sets.)

The following is a sketch of the likelihood calculation for an example 
photometric selection criterion, which should serve as a useful guide once the criteria are fixed.
The criterion is for $\ge N$ photometric points
above a signal-to-noise threshold (translating to a distinct limiting signal $n_{0i}$
for measurement $i$ of a given transient) given $M$ available measurements. 
The fail/pass status of the measurements are stored as 0/1 in an array $b$.
There are $\sum_{k=N}^M \binom{M}{k}$ 
distinct $b$'s that allow acceptance of the light curve.  In the notation $b_{ijk}$, $i$ indexes
the configuration, $j$ the transient, and $k$ the photometric point of transient $j$.

\subsubsection{Likelihood for the {\it obs} Set}
The likelihood for the {\it obs} set is
\begin{multline}
p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  \sigma_\beta, Z, g, g_N, f_g)\\
= \sum_i \int_L dL\, p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G , b_i|  L, \ldots)
 P(L|\ldots) \\
 \propto \sum_i  \epsilon(n_{SN}; b_{i}) \int_L dL\, p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G|  L, \ldots)P(L|\ldots).
\end{multline} 
It is proportional to the truncated likelihood of the underlying sample, where the truncation
is achieved through $\epsilon(n_{SN}; b_{i})$, the efficiency that a light curve is 
selected in for a given configuration.  For the limiting flux criteria
\begin{equation}
\epsilon(n_{SN}; b_{i})= \prod_{jk}\mathcal{H}\left((-1)^{b_{ijk}+1}(n_{SN,jk}-n_{0,jk})\right),
\end{equation}
where $\mathcal{H}$ is the Heaviside step function; when $b_{ijk}=1$ the step in the efficiency
is up and for $b_{ijk}=0$ the step is down.

%The likelihood without the configuration condition for our measurements is
%\begin{multline}
%p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G | L, \ldots) \\
%= \delta(z_S - g_z) \delta(\theta_S-\theta_T) \delta(\theta_G -g) \delta(T_S-T)  \mathcal{N}
%\left(n_{SN} -\overline{n}_j(L ,\ldots), C_P \right).
%\end{multline}. 
%

%
%The probability for failing (passing) the selection criterion for a single point is
%\begin{equation}
%P(b_{ij} | L, \ldots) = b_{ij} + (-1)^{b_{ij}}\int_{-\infty}^{ADU_0} dn_{SN,i}  \mathcal{N}\left(n_{SN} - \overline{n}_j(L ,\ldots), C_P \right),
%\end{equation}
%the (complementary) cumulative distribution function for a normal distribution
%with variable
%$n_0$, i.e.\ 2 times the error function.

For measurements described in \S\ref{measurements:sec}, the likelihood for the {\it obs} Set is
\begin{multline}
p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \Omega_M, w, r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  \sigma_\beta, Z, g, g_N, f_g)\\
\propto \sum_i  \epsilon(n_{SN}; b_{i})  \int_L dL\, 
\mathcal{N}\left(n_{SN} - \overline{n}_j(L ,
g_z=z_S, \theta_T=\theta_S, g=\theta_G, T=T_S, \ldots), C_P \right)\\
P(L|g_z=z_S, \theta_T=\theta_S, g=\theta_G, T=T_S, \ldots),
\end{multline} 
where the latent parameters $T$, $\theta_T$ are not integrated over.
The normalization factor is parameter-dependent and is set by the condition
\begin{equation}
\sum_{T_S} \int dn_{SN}\,d{{z}}_S\,d\theta_{S}\,d\theta_G\,p(n_{SN}, {{T}}_S,{{z}}_S, \theta_{S}, \theta_G |  \ldots)=1.
\end{equation}

\subsubsection{Likelihood for the {\it mis} Set}
The likelihood for the {\it mis} set follow the same pattern as that of the
{\it obs} set except for not having to account for spectroscopic data.
\begin{multline}
p(n_{SN}, \theta_{G_1} |  \Omega_M, w, r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  \sigma_\beta, Z, g, g_N, f_g) \\
 \propto \sum_i  \epsilon(n_{SN}; b_{i}) 
\int_L dL\, 
\sum_k 
\pi_k\mathcal{N}\left(n_{SN} - \overline{n}_j(L ,
g=\theta_{G_k}, \ldots), C_P \right)
P(L|g=\theta_{G_k}, \ldots), 
\end{multline} 
where $\pi_k$ is the probability that the $k$'th galaxy is the host, provided by Ravi.

%\begin{multline}
%p(n_{SN}, \theta_G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
%= \sum_i \int_L dL\, p(n_{SN}, \theta_G | b_i, L, \ldots)
%P(b_{i} |L, \ldots) P(L|\ldots) ,
%\end{multline} 
%\begin{equation}
%p(n_{SN}, \theta_G | b_i, L, \ldots)
%  =  \frac{ \prod_j
% \epsilon(n_{SN,j}; b_{ij})
%  p(n_{SN}, \theta_G | L, \ldots)}
%  {\prod_j P(b_{ij}{ |L,\dots)}}.
%\label{misconf:eqn}
%\end{equation}

\section{Tasks}
\begin{table}[htdp]
\caption{default}
\begin{center}
\begin{tabular}{|c|c|}
\hline
Task/Deliverable & Responsible \\ \hline
Model Design & \\
Sampler &\\
Photometric Selection &\\
Spectroscopy Selection &\\
Host Galaxy Association &\\
Host Galaxy Parameters &\\
SN~Ia Models Selection &\\
Non-Ia Models Selection &\\
SN light curves ($n$) &\\
Photometric Zeropoints &\\
\hline
\end{tabular}
\end{center}
\label{Tasks and Responsible Parties}
\end{table}%

@@
